Real Time Fluid Simulation \\ \smaller using Smoothed-Particle Hydrodynamics and OpenGL

### 2014-12-13 paper/paper.tex

\section{History}
%
\hspace{6 pt} Given all the different applications for Smoothed Particle Hydrodynamics (SPH),
it was first used to simulate interstellar phenomena. Conceived in 1977 by Gingold and 
Monaghan was an improvement to the Standard Finite Difference Method, which until their 
breakthrough, was the method to use to simulate astrophysical phenomena. They improved 
on this method by making "use of Lagrangian description of fluid flow which automatically 
focuses attention on fluid elements" \cite{sphastrophysics}. In this implementation, particles 
"move according to the Newtonian equations with forces due to the pressure gradient and 
other body forces: gravity, rotation and magnetic" \cite{sphastrophysics}.
\\
\hspace*{6 pt} The result of Gingold and Monaghan's theory and implementation was a robust 
and extendable idea that could easily made more accurate "by increasing the number of particles 
and by using the devices known to improve Monte Carlo integration methods" \cite{sphastrophysics}.
%

>>>>

\section{History}
%
\hspace{6 pt} Given all the different applications for Smoothed Particle Hydrodynamics (SPH),
it was first used to simulate interstellar phenomena. Conceived in 1977 by Gingold and 
Monaghan was an improvement to the Standard Finite Difference Method, which until their 
breakthrough, was the method to use to simulate astrophysical phenomena. They improved 
on this method by making "use of Lagrangian description of fluid flow which automatically 
focuses attention on fluid elements" \cite{sphastrophysics}. In this implementation, particles 
"move according to the Newtonian equations with forces due to the pressure gradient and 
other body forces: gravity, rotation and magnetic" \cite{sphastrophysics}.
\\
\hspace*{6 pt} The set of equations utilized in Gingold and Monaghan's SPH implementation 
is a density distribution calculated at each point
\begin{align}
	\rho_s(r) = \int W(r - r') \rho(r') dr'
\end{align}
where W is a function satisfying the condition
\begin{align}
\int W(r) dr = 1
\end{align}
\hspace*{6 pt} This density distribution equation is used to calculate the density of the 
particles surrounding the current particle the equation it's being applied to.
\hspace*{6 pt} A Gaussian function is used for the kernel function, with the form
\begin{align}
\exp{\frac{-r^2}{h^2}}
\end{align}
where h is
\begin{align}
h = b(<r^2> - <r>^2)^\frac{1}{2}
\end{align}
and \textit{b} is adjustable.
\hspace*{6 pt} The gravitational potential of the particles is denoted by
\begin{align}
\phi = - G \int \frac{\rho_N(r')}{|r - r'|} dr'
\end{align}
\\
\hspace*{6 pt} The result of Gingold and Monaghan's theory and implementation was a robust 
and extendable idea that could easily made more accurate "by increasing the number of particles 
and by using the devices known to improve Monte Carlo integration methods" \cite{sphastrophysics}.
%

\section{Smoothed Particle Hydrodynamics Overview}
%

%
